### 2025-07-09 README.Rmd
slightly modeified readme

hsargs <- checkhsargs(hsargs) # lists chosen options before run, only for TAS 
# if you want to check your own set then include a suitable check function 
# within your jurisdiction's HS source file or package (see EGHS as example).

@@

```{r,  echo=TRUE, eval=FALSE}
library(codeutils)
library(aMSE)
dropdir <-getDBdir()   # once again FIX this to suit your own directory setup.
prefixdir <- pathtopath(dropdir,"/A_codeR/aMSETas/scenarios/")
filelist=c("controlEG.csv","lf_WZ90-20.csv","saudataEG.csv")
aMSE::copyto(prefixdir=prefixdir,fromdir="EG",todir="EGconst",
              filelist=filelist)
# this copies the files across and renames them appropriately.
```

The change in the harvest strategy is implemented in the hsargs rather than in the code, although it is necessary to let the do_MSE() funciton know of the change:

@@

# current Tas HS
hsargs <- list(mult=0.025, # cpue range expansion factor when calc the targqnt
               wid = 4, # number of years in the grad4 PM
               targqnt = 0.55, # quantile defining the cpue target
               maxtarg = c(150,150,150,150,150,150,150,150), # max cpue Target
               acatch =  c(22,48,26,125,105,210,175,47),#ONLY used for consthcr
               pmwts = c(0.65,0.25,0.10),  # relative weights of PMs default
               hcr = c(0.25,0.75,0.8,0.85,0.9,1,1.05,1.1,1.15,1.2), 
               hcrm3 = c(0.25,0.75,0.8,0.85,0.9,1,1.1,1.2,1.25,1.3),
               #hcr = c(1,1,1,1,1,1,1,1,1,1,1), # multipliers for constant catch
               startCE = 2000, # used in constant reference period HS
               endCE = 2019,   # used in constant reference period HS
               #refperiodCE = 2000:2019, # use a vector of years instead
               metRunder = 2,  # MR2 if CE below targ multTAC = 1
               metRover = 2,   # MR1 CE>targ for 2+ yrs before multTAC increases
               decrement=1, # use fishery data up to the end of the time series
               pmwtSwitch = 4, # number of years after reaching the targCE to
               stablewts = c(0.65, 0.25, 0.1), # replace pmwts with stablewts
               hcrname="consthcr", # name of HCR: constantrefhcr / consthcr
               printmat=NULL)

hsargs <- checkhsargs(hsargs)

out <- do_MSE(rundir,controlfile,hsargs=hsargs,hcrfun=consthcr,  # constantrefhcr,     #
              sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
              getdata=constdata,calcpopC=calcexpectpopC,makeouthcr=makeoutconst,
              fleetdyn=NULL,scoreplot=plotfinalscores,
              plotmultflags=plotmultandflags,interimout="",
              varyrs=7,startyr=38,verbose=TRUE,ndiagprojs=4,cutcatchN=56,
              matureL=c(40,170),wtatL=c(50,200),mincount=120,
              includeNAS = FALSE,depensate=0,kobeRP=c(0.4,0.2,0.15),
              nasInterval=1,minsizecomp=c(100,135),uplimH=0.35,incH=0.005,
              deleteyrs=0)

>>>>

checkhsargs(hsargs) # lists chosen options before run, only for TAS 
# if you want to check your own set then include a suitable check function 
# within your jurisdiction's HS source file or package (see EGHS as example).

@@

```{r,  echo=TRUE, eval=FALSE}
library(codeutils)
library(aMSE)

# ONCE AGAIN YOU WILL NEED TO SETUP YOUR OWN DIRECTORY STRUCTURE  TO DEFINE
# THE prefixdir
dropdir <-getDBdir()   
prefixdir <- pathtopath(dropdir,"/A_codeR/aMSETas/scenarios/")
filelist=c("controlEG.csv","lf_WZ90-20.csv","saudataEG.csv")
aMSE::copyto(prefixdir=prefixdir,fromdir="EG",todir="EGconst",
              filelist=filelist)
# this copies the files across and renames them appropriately.
# NO CHANGES ARE NEEDED IN THE FILES BECAUSE THE CHANGES OCCUR IN hsargs
```

The change in the harvest strategy is implemented in the hsargs rather than in the code, although it is necessary to let the do_MSE() function know of the change:

@@

# current Tas HS
hsargs <- list(mult=0.025, # cpue range expansion factor when calc the targqnt
               wid = 4, # number of years in the grad4 PM
               targqnt = 0.55, # quantile defining the cpue target
               maxtarg = c(150,150,150,150,150,150,150,150), # max cpue Target
               acatch =  c(22,48,26,125,105,210,175,47),#ONLY used for consthcr
               pmwts = c(0.65,0.25,0.10),  # relative weights of PMs default
               hcr = c(0.25,0.75,0.8,0.85,0.9,1,1.05,1.1,1.15,1.2), 
               hcrm3 = c(0.25,0.75,0.8,0.85,0.9,1,1.1,1.2,1.25,1.3),
               startCE = 2000, # used in constant reference period HS
               endCE = 2019,   # used in constant reference period HS
               metRunder = 2,  # MR2 if CE below targ multTAC = 1
               metRover = 2,   # MR1 CE>targ for 2+ yrs before multTAC increases
               decrement=1, # use fishery data up to the end of the time series
               pmwtSwitch = 4, # number of years after reaching the targCE to
               stablewts = c(0.65, 0.25, 0.1), # replace pmwts with stablewts
               hcrname="consthcr", # name of HCR: constantrefhcr / consthcr
               printmat=NULL)

checkhsargs(hsargs)

# NOTE THE CHANGE FROM tasdata TO constdata AND makeouthcr TO makeoutconst 
# IN THIE THIRD LINE
out <- do_MSE(rundir,controlfile,hsargs=hsargs,hcrfun=consthcr,  # constantrefhcr,     #
              sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
              getdata=constdata,calcpopC=calcexpectpopC,makeouthcr=makeoutconst,
              fleetdyn=NULL,scoreplot=plotfinalscores,
              plotmultflags=plotmultandflags,interimout="",
              varyrs=7,startyr=38,verbose=TRUE,ndiagprojs=4,cutcatchN=56,
              matureL=c(40,170),wtatL=c(50,200),mincount=120,
              includeNAS = FALSE,depensate=0,kobeRP=c(0.4,0.2,0.15),
              nasInterval=1,minsizecomp=c(100,135),uplimH=0.35,incH=0.005,
              deleteyrs=0)
